---
title: "Tesla Stocks Shiny App Presentation"
author: "Katie Chai"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set()
```

<style>
pre {
  font-size: 20px;
  line-height: 22px;
}
p {
  margin-top: -10px;
}
</style>

## Overview

<font size="5">
'teslastocks_app' is a Shiny app that looks at Tesla's stock data from 2010 to 2020. There are four different styles of plots available: candlestick, OHLC (open high low close), line, and area.

There is only one dataset used in this app: the 'TSLA.csv' file that was originally obtained from the 'Tesla stock data from 2010 to 2020' dataset on Kaggle by Timo Bozsolik. It was obtained from this [page](https://www.kaggle.com/datasets/timoboz/tesla-stock-data-from-2010-to-2020).

The loading of necessary libraries is shown below:

```{r, message=FALSE}
library(shiny); library(shinythemes); library(shinyWidgets)
library(tidyverse); library(plotly)
```
</font>

## Data

<font size="4">
The dataset has seven variables, but only five of these are of interest in this app (Date, Open, High, Low, Close). The dataset was already in a tidy format so it did not need any cleaning, only the conversion of the Date column from character format to date format. A summary of the dataset is shown below:

```{r, echo=FALSE}
tsla <- read.csv("./data/TSLA.csv")
tsla <- tsla %>%
  mutate(Date=as.Date(Date, format="%Y-%m-%d"))
```

```{r, comment=""}
summary(tsla)
```
</font>

## Inputs and Outputs

<font size="5">
There are two inputs and one output in this app: a plot type input (using `pickerInput()`), a date range input (using `sliderInput()`), and a plotly output (using `plotlyOutput()`).

The candlestick plot portion of the code for defining the output is shown below as an example:

```{r, eval=FALSE}
output$stockplot <- renderPlotly({
  if (input$type == "Candlestick"){
    fig <- tsla %>%
      filter(Date >= input$daterange[1] & Date <= input$daterange[2]) %>%
      plot_ly(type="candlestick", x=~Date,
              open=~Open, close=~Close, high=~High, low=~Low) %>%
      layout(xaxis=list(rangeslider=list(visible=FALSE), type="date"), 
             yaxis=list(autorange=TRUE))
  }
})
```
</font>

## Plot Example

<font size="4">
A candlestick plot corresponding to the entire range of dates is shown below as an example of the plot output.

```{r, echo=FALSE, out.height="100%"}
tsla %>%
  plot_ly(type="candlestick", x=~Date,
          open=~Open, close=~Close, high=~High, low=~Low) %>%
  layout(xaxis=list(rangeslider=list(visible=FALSE), type="date"), 
         yaxis=list(autorange=TRUE), 
         title=paste("TSLA Stocks", min(tsla$Date), "to", max(tsla$Date)), 
         hovermode="x") %>%
      config(modeBarButtonsToRemove=c("zoom2d", "select2d", "lasso2d"))
```
</font>



